Linear instability underlying synchronous waving of marine grass in flow

### 2014-08-29 Paper/grass.tex

Comparison of frequency associated with mode of highest growth predicted by model with that of experimental observations of frequencies in the lab scale experiments, for cases where the vegetation was sufficiently dense to be modeled by a continuum drag field, is shown in Figure \ref{Observed_calculated}. The observed frequencies are associated with the peaks in velocity spectra, frequency of monami and frequency of vortex passage. The deviation of predicted frequency from the observed can be attributed to the various simplification we have made in our model. In a real canopy, the drag coefficients are known to
vary from bottom to tip of the grass blades\cite{Vivoni98,Nepf00}. The turbulent viscosity is also known to vary between the flow of unvegetated region and flow through the canopy. Although these variation
are not central to the mechanism leading to the instability of flow, we believe an improved analysis of flow with these variation in the model might lead to a better agreement between the
observed frequency and the predicted frequency.

>>>>

Comparison of frequency (Im$(\sigma)$) of the fastest ggrowing mode with that of experimental observations of frequencies in the lab scale experiments, for cases where the vegetation was sufficiently dense to be modeled by a continuum drag field, is shown in Figure \ref{Observed_calculated}. The observed frequencies are associated with the peaks in velocity spectra, frequency of monami and frequency of vortex passage \shreyas{cite someone}. The deviation of predicted frequency from the observed can be attributed to the various simplification we have made in our model. In a real canopy, the drag coefficients are known to
vary from bottom to tip of the grass blades\cite{Vivoni98,Nepf00}. The turbulent viscosity is also known to vary between the flow of unvegetated region and flow through the canopy. Although these variation
are not central to the mechanism leading to the instability of flow, we believe an improved analysis of flow with these variation in the model might lead to a better agreement between the
observed frequency and the predicted frequency.
